DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-16 ase2017/paper.tex
added comments in the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%\textcolor{red}{add more for the second approach}

@@

>>>>

\textcolor{red}{Dario: Can you please expand a bit further the second approach}

@@

\textcolor{red}{Pascal: May I ask you to briefly mention the modules and also the LOC associated to each module? The tool paper reviewers usually like to know about the tool's complexity (i.e., number of modules/components and LOC).}
